\cvSection[folder-open]{Projects}

\begin{cvHeadingList}

  \cvProjectHeading{Automated UI Tests}{Java, JUnit, Selenium, Selenoid, Docker}{May 2022}

  \begin{cvList}
    \cvItem Generated use cases, developed test coverage based on
      them, and conducted functional testing of the website interface.
    \cvItem Utilized Selenide framework (wrapper for Selenium
      WebDriver) to write an automated UI tests and Selenoid (Selenium
      Grid alternative) to run different versions of browsers in
      docker containers. Also used the Allure framework to generate
      test reports.
  \end{cvList}

  \cvProjectHeading{Image Rotator}{Assembly, C}{December 2021}

  \begin{cvList}
    \cvItem Created an application in C that allows to rotate bitmap
      images by 90 degrees counterclockwise.
    \cvItem Developed a new module called sepia filter that makes an
      image with vivid colors look like an old. The module was written
      in assembly language to improve the performance of the program.
      Most of graphical editors include a filter like this.
  \end{cvList}

  \cvProjectHeading{Point-Hit Checker}{Java, Spring, Oracle, JavaScript, React}{December 2020}

  \begin{cvList}
    \cvItem Developed a web-application using Spring Boot and React
      that checks if a point falls into the given area on the
      coordinate plane. The interaction between the back-end and
      front-end levels was organized through the REST API.
    \cvItem Supported token based authentication with JWT using Spring
      Security to keep the user logged in and prevent unauthorized
      access.
    \cvItem Used Spring Data with Hibernate to access the database
      managed by Oracle DBMS, where stored all verification results.
  \end{cvList}

  \cvProjectHeading{Collection Manager}{Java, JavaFX, PostgreSQL}{April 2020}

  \begin{cvList}
    \cvItem Designed a console application that implements interactive
      management of a collection of objects stored in a CSV file.
    \cvItem Devided the program into client and server modules. The
      server module executes commands for managing the collection and
      the client module interactively reads commands, passes them to
      the server for execution, and displays the results of execution.
    \cvItem Improved server performance by adding support for
      multi-threaded request processing and using a database instead
      of a CSV file.
    \cvItem Used JavaFX to create a GUI for the client module that
      supports commands to manipulate the collection. The GUI also
      supports internationalism and localization for the following
      languages: English, Spanish (Costa Rica), Russian, and Belarusian.
  \end{cvList}

\end{cvHeadingList}
